{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-11-30 thesis/education.tex
David A. Eckhardt
dodge latex changebar bug
fix a bunch of citations; convert bib to alpha
add short versions of fig/tab capts for frontmatter list

This section presents the user studies done in
%CMU's 15-410 and PSU's \psuos classes,
%in semesters Fall 2015 to Spring 2018 and in Spring 2018 alone, respectively,
%taught by David Eckhardt and Timothy Zhu, respectively.
CMU's 15-410 in semesters Fall 2015 to Spring 2018,
taught by David Eckhardt,
and in PSU's \psuos in Spring 2018,
taught by Timothy Zhu.
In both cases the instructors assisted to introduce me during the guest lecture
%(see below)
and to distribute the recruiting emails;
TAs were not involved.
The in-house user study has CMU IRB approval under study number STUDY2016\_00000425,
and the external user study under STUDY2017\_00000429.

@@

\begin{table}[h]
	\begin{center}
		% ugh this looks so stupid
		% but better than latex's output looking stupid
		\begin{tabular}{r|crcrc|r}
			& \multicolumn{5}{c|}{\bf Used Landslide?} & \\
			\bf Semester & & \bf yes & & \bf no & & \bf Total \\
			\hline
			% group-[redacted] had a p2/ dir, but not in grade files
			CMU S'15	& &   8	& &  18	& &  26 \\
			CMU F'15	& &  22	& &   8	& &  30 \\
			CMU S'16	& &  18	& &  16	& &  34 \\
			CMU F'16	& &  12	& &   6	& &  18 \\
			CMU S'17	& &  19	& &  13	& &  32 \\
			CMU F'17	& &  14	& &   5	& &  19 \\
			CMU S'18	& &  10	& &   8	& &  18 \\
			\hline
			U. Chicago F'17	& &   4	& &  17	& &  21 \\ % 21 taken from number of submitted 'threads', idk abt userprog
			PSU S'18	& &  38	& &  98	& & 136 \\
			\hline
			\bf CMU total	& & 103	& &  74	& & 177 \\
			\bf Non-CMU total
					& &  42	& & 115	& & 157 \\
			\bf Total	& & 145	& & 189	& & 327 \\
		\end{tabular}
	\end{center}
	\caption{Participation rates across semesters,
	among students who submitted thread libraries (CMU, PSU) or kernels (U. Chicago).}
	\label{tab:photo-of-ze-studence}
\end{table}

@@

			% this 1 for f17 was salvaged from results-raw; the grupo who had it it was their only bug
			% and it was an invl heap that i think came from multiple landslides
			% (and i hadn't listed them as "fixing" it; they were listed as det 1 race 0 fixed 0)
			% so i'm -1ing for "det bugs found" and "groups w any bugs found" to compensate
			Known false positives	& 1	& 2	& 6	& 5	& 3	& 1	& 0	& 18 	\\
			\hline
			Deteterministic bugs found ($\le$)
						& 5	& 20	& 18	& 18	& 30	& 15	& 9	& 115	\\
			Concurrency bugs found	& 5	& 56	& 19	& 15	& 13	& 9	& 5	& 122	\\
			\bf Total bugs found	& 10	& 76	& 37	& 33	& 43	& 24	& 14	& 237	\\
			\hline
			Deteterministic bugs fixed ($\ge$/$\le$)
						& 3	& 19	& 9	& 15	& 22	& 12	& 7	& 87	\\
			Concurrency bugs fixed ($\ge$)
						& 1	& 38	& 11	& 10	& 12	& 4	& 4	& 80	\\
			\bf Total bugs fixed	& 4	& 57	& 20	& 25	& 34	& 16	& 11	& 167	\\
	\end{tabular}
	\end{center}
	\caption{Landslide's bug-finding performance across all semesters of the CMU 15-410 study.
	$\le$ marks possible overcounts on account of unidentified false positives;
	$\ge$ marks possible undercounts on account of students not necessarily re-running to verify bugfixes.}
	\label{tab:cmubugs}
\end{table}

@@

% colors for these graphs in case i need them again later
% #720000
% #FF8080
% #804700
% #FFC680
% #807700
% #FFF780
% #004111
% #ABFFC0
% #002680
% #ABC3FF
% #3B0144
% #F4ABFF
\begin{figure}[p]
	\begin{center}
	\begin{tabular}{c}
		\includegraphics[width=0.96\textwidth]{photo-of-ze-studence.pdf}
		\\
		(a) Visualized as a box plot.
		\\
		\\
		\includegraphics[width=0.96\textwidth]{photo-of-ze-studence-cdf.pdf}
		\\
		(b) Visualized as an EDF.
	\end{tabular}
	\end{center}
	\caption{Distribution of project grades among Landslide users and non-users.
	Study participants (S'15 to S'18) are the experimental group;
	non-participants (S'15 to S'18)
	and students from semesters predating the study (F'13-F14) are the control groups.
	Compare Landslide users to non-users for within-semester differences,
	or users to pre-study students to mitigate selection bias.}
	\label{fig:photo-of-ze-studence}
\end{figure}

@@

% TODO check figure placement
\begin{table}[t]
	\begin{center}
		\small
		% note, smth like fisher's method which "combines independent studies into a meta p value"
		% cannot be applied for 2 reasons - 1, these are not independent since the same studence were
		% running landslide on diff test cases; 2, the hypotheses tested are different for each test
	\begin{tabular}{r||cc|cc|c|cc}
		& \multicolumn{2}{c|}{\bf Landslide users} & \multicolumn{2}{c|}{\bf Non-users} & & \multicolumn{2}{c}{\bf Significance} \\
		\bf Bug name & \bf \#correct & \bf \#buggy & \bf \#correct & \bf \#buggy & \bf $\Delta$\%correct & $p$ & \bf cutoff \\
		\hline
		% calculated in R with (rest done similarly)
		% fisher.test(rbind(c(11,10),c(0,16)))$p.value --> 0.0006143355
		Exit UAF  & 11	& 10	& 0	& 16	& $+52.4\%$	& 0.00061	& 0.0125 \\
		% I spent more hours than I should have looking at this landslide-user-submitted-bug group.
		% Can't name the group here, but if you're me and have the analysis file,
		% it's the one from f17 with 3 mutex_test logs in their "u" snapshot.
		% It seems like a mysterious older version of mutex.c was present between their "a" version
		% (which gets fully verified very quickly btw) and their "u" version (for which landslide finds
		% the bug in just a few minutes, no way they could be running the same version; plus the reported
		% data races and so on in the id-log don't line up to the "u" mutex.c source code).
		% That version was correct, then they updated it (introducing the bug) and ran a bunch of other tests,
		% but didn't rerun mutex_test to check their update.
		Mutex     & 17	& 1	& 19	& 0	& $-05.6\%$	& 0.49 & 0.0125 \\
		Paraguay  & 20	& 1	& 14	& 2	& $+07.7\%$	& 0.57	& 0.0125 \\
		% nb this is any downgrade related ding not just dgr tested ones
		% nb 1 is msising bc didn't impl rwlock at all
		% nice p value
		Downgrade & 10	& 3	& 19	& 4	& $-05.7\%$	& 0.69	& 0.0125 \\ % TODO verify these buggers by eye
		\hline
		\bf Total & 58	& 15	& 52	& 22	& $+09.2\%$	& 0.26 & 0.05 \\
	\end{tabular}
	\end{center}
	\caption{
		Correlation of student Landslide use with solving certain bugs in their final submission during Fall 2017 and Spring 2018 semesters.
		%$\Delta P$ stands for the increased probability that a student submits a correct P2
		%(with respect to each bug)
		%given that they use Landslide, versus not using Landslide; i.e.,
		%$P(\mathsf{correct}|\mathsf{landslide})-
		%P(\mathsf{correct}|\mathsf{non\text{-}user})$.
		Note that the totals in the bottom row double-count students,
		which makes sense only if you believe the incidences of each bug in a given submission are independent.
		}
	\label{tab:eval-common-bugs}
\end{table}

@@

\begin{figure}[p]
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=0.42\textwidth]{survey1.pdf} &
			\includegraphics[width=0.42\textwidth]{survey2.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey3.pdf} &
			\includegraphics[width=0.42\textwidth]{survey4.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey5.pdf} &
			\includegraphics[width=0.42\textwidth]{survey6.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey7.pdf} &
			\includegraphics[width=0.42\textwidth]{survey8.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey9.pdf} &
			\includegraphics[width=0.42\textwidth]{survey10.pdf} \\
		\end{tabular}
	\end{center}
	\caption{Student survey responses.
	SD/D/N/A/SA stands for
	strongly disagree/\allowbreak{}disagree/\allowbreak{}neutral/\allowbreak{}agree/\allowbreak{}strongly agree.}
	\label{fig:survey}
\end{figure}

@@

\begin{enumerate}
	\item Requested for preemption traces to be more clear about the meaning of each stack trace in each table cell,
		and complained of inaccurate line numbers
		[likely referring to how the current behaviour indicates the line of code {\em after} a function call,
		corresponding to the {\tt call} instruction's pushed return address,
		rather than the function call itself]. [This answer from CMU; see above.]
	\item Including a manual or tutorial would be helpful [presumably beyond the user guide's instructions, such as recapping the procedure shown in the lecture demo which wasn't written down anywhere].
	\item Don't print warnings about line length exceeding 80 characters [inconsistency between 15-410 and \psuos compilation options].
	\item ``It takes too long. But I guess that's impossible to fix.'' [Well, it's an open research problem to fix!]
	\item Preemption traces should explicitly indicate where in the interleaving the bug occurred.
		[Root cause identification is its own research area, but more detail is certainly possible.]
	\item Improve explanation of data races [in the user guide, perhaps].
	\item Happy with it as-is [\revisionminor{reported by three} students]
	\item [\revisionminor{Seven non-respondents}]
\end{enumerate}

@@

Comparing the survey response distributions between CMU versus PSU and U. Chicago (Figure~\ref{fig:survey}),
CMU students tended to verify their bugfixes more often by re-running Landslide
and found the preemption traces easier to understand,
while PSU and U. Chicago students generally compared Landslide more favourably to stress testing
(CMU students comparatively preferred the more nuanced answer that it depends on the type of bug),
and reported more often that \revisionminor{it} helped them understand concurrency better.
%Considering that CMU's 15-410 demands substantial prerequisite concurrency experience
%(15-213 \cite{sigcse01:CSaPP} or equivalent)
%whereas PSU's \psuos is more towards the average between CMU's 15-213 and 15-410
%(tempering the difficulty of P2 to make it more accessible (\sect{\ref{sec:overview-psu}})),
Considering the higher demand CMU's 15-410 makes for prerequisite concurrency experience
compared to PSU's relative tempering of P2's difficulty to make it more accessible (\sect{\ref{sec:pebbles}}),
% TODO: represent u c in this sentents?
these trends seem to correlate with the different levels of preparation each course's students had,
showing that students of various skill levels
can each benefit from the experience in different ways.

>>>>

This section presents the user studies done in
%CMU's 15-410 and PSU's \psuos classes,
%in semesters Fall 2015 to Spring 2018 and in Spring 2018 alone, respectively,
%taught by David A. Eckhardt and Timothy Zhu, respectively.
CMU's 15-410 in semesters Fall 2015 to Spring 2018,
taught by David A. Eckhardt,
and in PSU's \psuos in Spring 2018,
taught by Timothy Zhu.
In both cases the instructors assisted to introduce me during the guest lecture
%(see below)
and to distribute the recruiting emails;
TAs were not involved.
The in-house user study has CMU IRB approval under study number STUDY2016\_00000425,
and the external user study under STUDY2017\_00000429.

@@

\begin{table}[h]
	\begin{center}
		% ugh this looks so stupid
		% but better than latex's output looking stupid
		\begin{tabular}{r|crcrc|r}
			& \multicolumn{5}{c|}{\bf Used Landslide?} & \\
			\bf Semester & & \bf yes & & \bf no & & \bf Total \\
			\hline
			% group-[redacted] had a p2/ dir, but not in grade files
			CMU S'15	& &   8	& &  18	& &  26 \\
			CMU F'15	& &  22	& &   8	& &  30 \\
			CMU S'16	& &  18	& &  16	& &  34 \\
			CMU F'16	& &  12	& &   6	& &  18 \\
			CMU S'17	& &  19	& &  13	& &  32 \\
			CMU F'17	& &  14	& &   5	& &  19 \\
			CMU S'18	& &  10	& &   8	& &  18 \\
			\hline
			U. Chicago F'17	& &   4	& &  17	& &  21 \\ % 21 taken from number of submitted 'threads', idk abt userprog
			PSU S'18	& &  38	& &  98	& & 136 \\
			\hline
			\bf CMU total	& & 103	& &  74	& & 177 \\
			\bf Non-CMU total
					& &  42	& & 115	& & 157 \\
			\bf Total	& & 145	& & 189	& & 327 \\
		\end{tabular}
	\end{center}
	\caption[Participation rates across semesters.]
		{Participation rates across semesters,
	among students who submitted thread libraries (CMU, PSU) or kernels (U. Chicago).}
	\label{tab:photo-of-ze-studence}
\end{table}

@@

			% this 1 for f17 was salvaged from results-raw; the grupo who had it it was their only bug
			% and it was an invl heap that i think came from multiple landslides
			% (and i hadn't listed them as "fixing" it; they were listed as det 1 race 0 fixed 0)
			% so i'm -1ing for "det bugs found" and "groups w any bugs found" to compensate
			Known false positives	& 1	& 2	& 6	& 5	& 3	& 1	& 0	& 18 	\\
			\hline
			Deteterministic bugs found ($\le$)
						& 5	& 20	& 18	& 18	& 30	& 15	& 9	& 115	\\
			Concurrency bugs found	& 5	& 56	& 19	& 15	& 13	& 9	& 5	& 122	\\
			\bf Total bugs found	& 10	& 76	& 37	& 33	& 43	& 24	& 14	& 237	\\
			\hline
			Deteterministic bugs fixed ($\ge$/$\le$)
						& 3	& 19	& 9	& 15	& 22	& 12	& 7	& 87	\\
			Concurrency bugs fixed ($\ge$)
						& 1	& 38	& 11	& 10	& 12	& 4	& 4	& 80	\\
			\bf Total bugs fixed	& 4	& 57	& 20	& 25	& 34	& 16	& 11	& 167	\\
	\end{tabular}
	\end{center}
	\caption[Landslide's bug-finding performance across all semesters.]
		{Landslide's bug-finding performance across all semesters of the CMU 15-410 study.
	$\le$ marks possible overcounts on account of unidentified false positives;
	$\ge$ marks possible undercounts on account of students not necessarily re-running to verify bugfixes.}
	\label{tab:cmubugs}
\end{table}

@@

% colors for these graphs in case i need them again later
% #720000
% #FF8080
% #804700
% #FFC680
% #807700
% #FFF780
% #004111
% #ABFFC0
% #002680
% #ABC3FF
% #3B0144
% #F4ABFF
\begin{figure}[p]
	\begin{center}
	\begin{tabular}{c}
		\includegraphics[width=0.96\textwidth]{photo-of-ze-studence.pdf}
		\\
		(a) Visualized as a box plot.
		\\
		\\
		\includegraphics[width=0.96\textwidth]{photo-of-ze-studence-cdf.pdf}
		\\
		(b) Visualized as an EDF.
	\end{tabular}
	\end{center}
	\caption[Distribution of project grades among Landslide users and non-users.]
		{Distribution of project grades among Landslide users and non-users.
	Study participants (S'15 to S'18) are the experimental group;
	non-participants (S'15 to S'18)
	and students from semesters predating the study (F'13-F14) are the control groups.
	Compare Landslide users to non-users for within-semester differences,
	or users to pre-study students to mitigate selection bias.}
	\label{fig:photo-of-ze-studence}
\end{figure}

@@

% TODO check figure placement
\begin{table}[t]
	\begin{center}
		\small
		% note, smth like fisher's method which "combines independent studies into a meta p value"
		% cannot be applied for 2 reasons - 1, these are not independent since the same studence were
		% running landslide on diff test cases; 2, the hypotheses tested are different for each test
	\begin{tabular}{r||cc|cc|c|cc}
		& \multicolumn{2}{c|}{\bf Landslide users} & \multicolumn{2}{c|}{\bf Non-users} & & \multicolumn{2}{c}{\bf Significance} \\
		\bf Bug name & \bf \#correct & \bf \#buggy & \bf \#correct & \bf \#buggy & \bf $\Delta$\%correct & $p$ & \bf cutoff \\
		\hline
		% calculated in R with (rest done similarly)
		% fisher.test(rbind(c(11,10),c(0,16)))$p.value --> 0.0006143355
		Exit UAF  & 11	& 10	& 0	& 16	& $+52.4\%$	& 0.00061	& 0.0125 \\
		% I spent more hours than I should have looking at this landslide-user-submitted-bug group.
		% Can't name the group here, but if you're me and have the analysis file,
		% it's the one from f17 with 3 mutex_test logs in their "u" snapshot.
		% It seems like a mysterious older version of mutex.c was present between their "a" version
		% (which gets fully verified very quickly btw) and their "u" version (for which landslide finds
		% the bug in just a few minutes, no way they could be running the same version; plus the reported
		% data races and so on in the id-log don't line up to the "u" mutex.c source code).
		% That version was correct, then they updated it (introducing the bug) and ran a bunch of other tests,
		% but didn't rerun mutex_test to check their update.
		Mutex     & 17	& 1	& 19	& 0	& $-05.6\%$	& 0.49 & 0.0125 \\
		Paraguay  & 20	& 1	& 14	& 2	& $+07.7\%$	& 0.57	& 0.0125 \\
		% nb this is any downgrade related ding not just dgr tested ones
		% nb 1 is msising bc didn't impl rwlock at all
		% nice p value
		Downgrade & 10	& 3	& 19	& 4	& $-05.7\%$	& 0.69	& 0.0125 \\ % TODO verify these buggers by eye
		\hline
		\bf Total & 58	& 15	& 52	& 22	& $+09.2\%$	& 0.26 & 0.05 \\
	\end{tabular}
	\end{center}
	\caption[Correlation of student Landslide use with solving certain bugs.]
		{
		Correlation of student Landslide use with solving certain bugs in their final submission during Fall 2017 and Spring 2018 semesters.
		%$\Delta P$ stands for the increased probability that a student submits a correct P2
		%(with respect to each bug)
		%given that they use Landslide, versus not using Landslide; i.e.,
		%$P(\mathsf{correct}|\mathsf{landslide})-
		%P(\mathsf{correct}|\mathsf{non\text{-}user})$.
		Note that the totals in the bottom row double-count students,
		which makes sense only if you believe the incidences of each bug in a given submission are independent.
		}
	\label{tab:eval-common-bugs}
\end{table}

@@

\begin{figure}[p]
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=0.42\textwidth]{survey1.pdf} &
			\includegraphics[width=0.42\textwidth]{survey2.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey3.pdf} &
			\includegraphics[width=0.42\textwidth]{survey4.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey5.pdf} &
			\includegraphics[width=0.42\textwidth]{survey6.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey7.pdf} &
			\includegraphics[width=0.42\textwidth]{survey8.pdf} \\
			\includegraphics[width=0.42\textwidth]{survey9.pdf} &
			\includegraphics[width=0.42\textwidth]{survey10.pdf} \\
		\end{tabular}
	\end{center}
	\caption[Student survey responses.]
		{Student survey responses.
	SD/D/N/A/SA stands for
	strongly disagree/\allowbreak{}disagree/\allowbreak{}neutral/\allowbreak{}agree/\allowbreak{}strongly agree.}
	\label{fig:survey}
\end{figure}

@@

\begin{enumerate}
	\item Requested for preemption traces to be more clear about the meaning of each stack trace in each table cell,
		and complained of inaccurate line numbers
		[likely referring to how the current behaviour indicates the line of code {\em after} a function call,
		corresponding to the {\tt call} instruction's pushed return address,
		rather than the function call itself]. [This answer from CMU; see above.]
	\item Including a manual or tutorial would be helpful [presumably beyond the user guide's instructions, such as recapping the procedure shown in the lecture demo which wasn't written down anywhere].
	\item Don't print warnings about line length exceeding 80 characters [inconsistency between 15-410 and \psuos compilation options].
	\item ``It takes too long. But I guess that's impossible to fix.'' [Well, it's an open research problem to fix!]
	\item Preemption traces should explicitly indicate where in the interleaving the bug occurred.
		[Root cause identification is its own research area, but more detail is certainly possible.]
	\item Improve explanation of data races [in the user guide, perhaps].
	\item Happy with it as-is [\revisionminor{reported by three} students]
		% wow, latex -- if you put [] outside of the revision, everything is awful forever
	\item \revisionminor{[Seven non-respondents]}
\end{enumerate}

@@

Comparing the survey response distributions between CMU versus PSU and U. Chicago (Figure~\ref{fig:survey}),
CMU students tended to verify their bugfixes more often by re-running Landslide
and found the preemption traces easier to understand,
while PSU and U. Chicago students generally compared Landslide more favourably to stress testing
(CMU students comparatively preferred the more nuanced answer that it depends on the type of bug),
and reported more often that \revisionminor{it} helped them understand concurrency better.
%Considering that CMU's 15-410 demands substantial prerequisite concurrency experience
%(15-213 \cite{csapp} or equivalent)
%whereas PSU's \psuos is more towards the average between CMU's 15-213 and 15-410
%(tempering the difficulty of P2 to make it more accessible (\sect{\ref{sec:overview-psu}})),
Considering the higher demand CMU's 15-410 makes for prerequisite concurrency experience
compared to PSU's relative tempering of P2's difficulty to make it more accessible (\sect{\ref{sec:pebbles}}),
% TODO: represent u c in this sentents?
these trends seem to correlate with the different levels of preparation each course's students had,
showing that students of various skill levels
can each benefit from the experience in different ways.

### 2018-11-30 thesis/landslide.tex
add short versions of fig/tab capts for frontmatter list

\begin{figure}[h]
	\begin{center}
	\begin{tabular}{l}
		\texttt{\ctype{void} \call{child}(\ctype{int} *xp) \{} \\
		\texttt{~~~~*xp++;} \\
		\texttt{\}} \\
		\\
		\texttt{\ctype{void} \call{parent}() \{} \\
		\texttt{~~~~\ctype{int} x = \const{0};} \\
		\texttt{~~~~\ctype{int} tid = \call{thr\_create}(child, \&x);} \\
		\texttt{~~~~x++;} \\
		\texttt{~~~~\call{thr\_join}(tid, \const{NULL});} \\
		\texttt{~~~~\flow{assert}{}(x == \const{2});} \\
		\texttt{\}} \\
	\end{tabular}
	\end{center}
	\caption{Example demonstrating the need for {\tt misbehave} to force the kernel
	to yield during {\tt thread\_fork}.}
	\label{fig:misbehave-example}
\end{figure}

@@

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{p{0.30\textwidth}p{0.30\textwidth}p{0.30\textwidth}}
	\begin{center}
	\begin{tabular}{l}
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		% old example, pre dpor-example figure
		%$T_1$@$t_a$: \texttt{write~x} \\
		%$T_2$@$t_b$: \texttt{read~y} \\
		%$T_2$@$t_c$: \texttt{read~x} \\
	\end{tabular}
	\end{center}
	&
	\begin{center}
	\begin{tabular}{l}
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		%$T_2$@$t_{b'}$: \texttt{read~y} \\
		%$T_2$@$t_{c'}$: \texttt{read~x} \\
		%$T_1$@$t_{a'}$: \texttt{write~x} \\
	\end{tabular}
	\end{center}
	&
	\begin{center}
	\begin{tabular}{l}
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		%$T_2$@$t_{b'}$: \texttt{read~y} \\
		%$T_1$@$t_{a''}$: \texttt{write~x} \\
		%$T_2$@$t_{c''}$: \texttt{read~x} \\
	\end{tabular}
	\end{center}
	\\
	\begin{center}
	(a) Original branch (C).
	\end{center}
	&
	\begin{center}
	(b) Goal branch (K).
	\end{center}
	&
	\begin{center}
	(c) Redundant branch (L).
	\end{center}
	\end{tabular}
	\end{center}
	\caption{Motivating example for the sleep sets optimization.
	Three of Figure~\ref{fig:dpor-example-2}'s interleavings are highlighted,
	with the always-independent {\tt tmpN++}s omitted for brevity.
	}
	\label{fig:sleepsets}
\end{figure}

@@

\begin{algorithm}[h]
	\ForEach{$S \in U$}{
		Execute($S$)
	}
	\caption{Straightforward exploration ordering}
	\label{alg:not-icb}
\end{algorithm}

@@

\begin{algorithm}[h]
	\For{$B \in [0..\mathsf{max}_P(U)]$}{
		\ForEach{$S \in U, P(S) \le B$}{
			Execute($S$)
		}
	}
	\caption{ICB exploration ordering}
	\label{alg:icb}
\end{algorithm}

>>>>

\begin{figure}[h]
	\begin{center}
	\begin{tabular}{l}
		\texttt{\ctype{void} \call{child}(\ctype{int} *xp) \{} \\
		\texttt{~~~~*xp++;} \\
		\texttt{\}} \\
		\\
		\texttt{\ctype{void} \call{parent}() \{} \\
		\texttt{~~~~\ctype{int} x = \const{0};} \\
		\texttt{~~~~\ctype{int} tid = \call{thr\_create}(child, \&x);} \\
		\texttt{~~~~x++;} \\
		\texttt{~~~~\call{thr\_join}(tid, \const{NULL});} \\
		\texttt{~~~~\flow{assert}{}(x == \const{2});} \\
		\texttt{\}} \\
	\end{tabular}
	\end{center}
	\caption[Example demonstrating the need for {\tt misbehave}.]
		{Example demonstrating the need for {\tt misbehave} to force the kernel
	to yield during {\tt thread\_fork}.}
	\label{fig:misbehave-example}
\end{figure}

@@

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{p{0.30\textwidth}p{0.30\textwidth}p{0.30\textwidth}}
	\begin{center}
	\begin{tabular}{l}
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		% old example, pre dpor-example figure
		%$T_1$@$t_a$: \texttt{write~x} \\
		%$T_2$@$t_b$: \texttt{read~y} \\
		%$T_2$@$t_c$: \texttt{read~x} \\
	\end{tabular}
	\end{center}
	&
	\begin{center}
	\begin{tabular}{l}
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		%$T_2$@$t_{b'}$: \texttt{read~y} \\
		%$T_2$@$t_{c'}$: \texttt{read~x} \\
		%$T_1$@$t_{a'}$: \texttt{write~x} \\
	\end{tabular}
	\end{center}
	&
	\begin{center}
	\begin{tabular}{l}
		\dporTBcode{tmp2 <- x (read)} \\
		\dporTAcode{tmp1 <- x (read)} \\
		\dporTAcode{x <- tmp1 (write)} \\
		\dporTBcode{x <- tmp2 (write)} \\
		%$T_2$@$t_{b'}$: \texttt{read~y} \\
		%$T_1$@$t_{a''}$: \texttt{write~x} \\
		%$T_2$@$t_{c''}$: \texttt{read~x} \\
	\end{tabular}
	\end{center}
	\\
	\begin{center}
	(a) Original branch (C).
	\end{center}
	&
	\begin{center}
	(b) Goal branch (K).
	\end{center}
	&
	\begin{center}
	(c) Redundant branch (L).
	\end{center}
	\end{tabular}
	\end{center}
	\caption[Motivating example for the sleep sets optimization.]
		{Motivating example for the sleep sets optimization.
	Three of Figure~\ref{fig:dpor-example-2}'s interleavings are highlighted,
	with the always-independent {\tt tmpN++}s omitted for brevity.
	}
	\label{fig:sleepsets}
\end{figure}

@@

\begin{algorithm}[h]
	\ForEach{$S \in U$}{
		Execute($S$)
	}
	\caption{Straightforward exploration ordering.}
	\label{alg:not-icb}
\end{algorithm}

@@

\begin{algorithm}[h]
	\For{$B \in [0..\mathsf{max}_P(U)]$}{
		\ForEach{$S \in U, P(S) \le B$}{
			Execute($S$)
		}
	}
	\caption{ICB exploration ordering.}
	\label{alg:icb}
\end{algorithm}
